### 2016-03-07 paper/icfp16-submission/evaluation.tex
update numbers

% \item \ES{others?}
%
\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{trace_size_step.png}
\includegraphics[width=\linewidth]{trace_size_jump.png}
\caption{Complexity of the generated traces. At least 90\% of the traces
  have a jump complexity of less than 10, with an average of 3.}
\label{fig:results-complexity}
\end{figure}
%

\paragraph{Results}
\label{sec:results-complexity}
The results of the experiment are summarized in
Figure~\ref{fig:results-complexity}.
%
The average number of single-step reductions per trace is 26 for the \ucsdbench\
dataset (27 for the \uwbench\ dataset) with a maximum of 2,744 (659 for
\uwbench). The average number of jumps per trace is 3 (also 3 for
\uwbench) with a maximium of 177 (52 for \uwbench). In both datasets at
least 90\% of the traces contain fewer than 10 jumps.
%

>>>>

% \item \ES{others?}
%
\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{trace_size_step.png}
\includegraphics[width=\linewidth]{trace_size_jump.png}
\caption{Complexity of the generated traces. 81\% of the combined traces
  have a jump complexity of at most 10, with an average of 7 and a
  median of 5.}
\label{fig:results-complexity}
\end{figure}
%

\paragraph{Results}
\label{sec:results-complexity}
The results of the experiment are summarized in
Figure~\ref{fig:results-complexity}.
%
The average number of single-step reductions per trace is 31 for the
\ucsdbench\ dataset (35 for the \uwbench\ dataset) with a maximum of
2,745 (660 for \uwbench) and a median of 16 (also 16 for \uwbench).
%
The average number of jumps per trace is 7 (also 7 for \uwbench) with a
maximium of 353 (105 for \uwbench) and a median of 4 (also 4 for
\uwbench).
%
In both datasets at least 80\% of the traces contain at most 10 jumps.
%

### 2016-03-07 paper/icfp16-submission/introduction.tex
update numbers

\paragraph{3. Evaluating Witnesses}
%
Of course, the problem of finding witnesses is
undecidable. In fact, due to the necessarily
conservative nature of static typing, there
may not even exist any witnesses for a given
ill-typed program.
%
Thus, our approach is a heuristic that is only useful
if it can find \emph{compact} witnesses for
\emph{real-world} programs.
%
Our third contribution is an extensive evaluation of our approach
on two different sets of ill-typed programs obtained by instrumenting
compilers used in beginner's classes~(\S~\ref{sec:evaluation}).
%
The first is the \uwbench\ data set~\cite{lerner_searching_2007}
comprising \uwsize\ ill-typed programs.
%
The second is a new \ucsdbench\ data set, comprising \ucsdsize\
ill-typed programs.
%
We show that for both data sets, our technique is able to generate
witnesses for nearly 90\% of the programs, in under a second in the
vast majority of cases.
%
Furthermore, we show that a simple interactive strategy yields
compact counterexample traces with fewer than 5 steps for 60\%
of the programs, and under 10 steps for 90\% of the programs.

>>>>

\paragraph{3. Evaluating Witnesses}
%
Of course, the problem of finding witnesses is
undecidable. In fact, due to the necessarily
conservative nature of static typing, there
may not even exist any witnesses for a given
ill-typed program.
%
Thus, our approach is a heuristic that is only useful
if it can find \emph{compact} witnesses for
\emph{real-world} programs.
%
Our third contribution is an extensive evaluation of our approach
on two different sets of ill-typed programs obtained by instrumenting
compilers used in beginner's classes~(\S~\ref{sec:evaluation}).
%
The first is the \uwbench\ data set~\cite{lerner_searching_2007}
comprising \uwsize\ ill-typed programs.
%
The second is a new \ucsdbench\ data set, comprising \ucsdsize\
ill-typed programs.
%
We show that for both data sets, our technique is able to generate
witnesses for nearly 90\% of the programs, in under a second in the
vast majority of cases.
%
Furthermore, we show that a simple interactive strategy yields
compact counterexample traces with at most 5 steps for 57\%
of the programs, and at most 10 steps for 81\% of the programs.
